\subsection{Discussion of results}
A reason for the big difference in homography estimation performance between SIFT and ORB might be how many feature points each find and are able to match. SIFT does find a considerable amount more features than ORB does, and because SIFT have more points, and point matches, it is able to estimate the homography better. RANSAC is used to eliminate outliers, which means even though SIFT might find more false positive matches, some are eliminated. It is likely SURF performs better than ORB for the same reason, however, because SURF produces worse descriptors (seen from nearest neighbour mean average precision) than SIFT, it is worse at estimating the homographies than SIFT.\\
The fact the mean localization error seems to be fairly high for all image descriptors might be due some aliasing or other approximation of the new location after moving the ground truth point locations into the coordinate system of the candidate points. If the new point location is off by 1 or 2 pixels it will make a quite big error in the mean localization error.\\
We see ORB and SIFT performs fairly well on nearest neighbour mean average precision, which is likely because they both are scale and rotation invariant, however, SURF is not rotation invariant, and this might be the reason it performs a lot worse. Another consideration when comparing nearest neighbour mean average precision is the length the descriptor vectors. SIFT creates a vector with length 128, ORB's descriptor vector length is 32 and SURF produces descriptors with length 64. When we measure the distance between these vectors the higher dimensional vectors are more likely to lie far away from each other. Having this in mind, SIFT seems to describe its features more accurately than ORB although their score is about the same.
