\begin{thebibliography}{9}
	\bibitem{wikimicroscopy}
	Wikipedia, 'Two-photon excitation microscopy', \url{https://en.wikipedia.org/wiki/Two-photon_excitation_microscopy}, Visited: June 11, 2021.
	
	\bibitem{trasnferlearning}
	Wikipedia, 'ImageNet', \url{https://en.wikipedia.org/wiki/ImageNet}, Visited: June 26, 2021.
	
	\bibitem{imaging}
	Mathiesen Janiurek et al, 'Apolipoprotein M-bound sphingosine-1-phosphate regulates blood–brain barrier paracellular permeability and transcytosis', eLife 2019, Published: 25 November 2019.

	\bibitem{swhati}
	Swathi Ayloo and Chenghua Gu, 'Transcytosis at the blood–brain barrier', Current Opinion in Neurobiology, Published: 2019.

	\bibitem{zhao}
	Zhen Zhao et al, 'Establishment and Dysfunction of the Blood-Brain Barrier', Cell 163, Published: November 19, 2015.
	
	\bibitem{confocal}
	Wikipedia, 'Confocal microscopy', \url{https://en.wikipedia.org/wiki/Confocal_microscopy}, Visited: June 22, 2021.
	
	\bibitem{unetarticle}
	Olaf Ronneberger et al, 'U-Net: Convolutional Networks for Biomedical Image Segmentation', Computer Science Department and BIOSS Centre for Biological Signalling Studies,
	University of Freiburg, Germany, Published: 2015.
	
	\bibitem{resnet}
	Kaiming He et al, 'Deep Residual Learning for Image Recognition', Microsoft Research, Published: December 10, 2015.
	
	\bibitem{linknet}
	A. Chaurasia and E. Culurciello, 'LinkNet: Exploiting Encoder Representations for Efficient Semantic Segmentation', Purdue University, Published: June 14, 2015
	
	\bibitem{augmentation}
	C. Shorten and T. Khoshgoftaar, 'A survey on Image Data Augmentation for Deep Learning', Journal of Big Data, Published: 2019.
	
	\bibitem{convolutionarticle}
	Vincent Dumoulin and Francesco Visin, 'A guide to convolution arithmetic for deep learning', MILA, Université de Montréal and AIRLab, Politecnico di Milano, March 24, 2016.
	
	\bibitem{adam}
	D.Kingma, J. Ba, 'ADAM: A METHOD FOR STOCHASTIC OPTIMIZATION', Published as a conference paper at ICLR, 2015
\end{thebibliography}